Appendix

### 2015-05-03 Rmarkdown/appendix.Rmd
Add software to appendix

## Software details

__TODO__

- R version
- `MethylationTuples`
- `methsim`
- `methtuples`
- others

__TODO: Add citations of all packages used in thesis__

>>>>

\section{Software details}\label{app:software_details}

The analyses described in my thesis made extensive use of R (`R Under development (unstable) (2014-10-29 r66891)` and `R version 3.2.0 (2015-04-16)`) and Python (`v2.6.6`). All analyses were run on one of the servers described above. The scripts used to prepare the results for each chapter are available from \url{https://github.com/PeteHaitch/phd_thesis_analyses}. Further details of software used are available in Appendix \ref{app:software_details}.

I developed several pieces of software during my PhD. These are listed in below, along with the version used in for analyses in my thesis:

- `methtuple` (`v1.4.0`)
- `GenomicTuples` (`v1.2.1`)
- `MethylationTuples` (`v0.3.0.9007`)
- `methsim` (`v0.5.0.9013`)

In addition, I made use of the R packages listed in Table \ref{tab:R_packages} and gratefully acknowledge the developers.

```{r R_packages, echo = FALSE, eval = TRUE, message = FALSE, results = "asis"}
library(xtable)
x <- read.table("../data/r_packages.txt",  header = TRUE,
                stringsAsFactors = FALSE, sep = "\t")
# Drop packages with "*" column set, which indicates the package is a
# "dependency of a dependency".
x <- x[x[, 2] != "*", ]
x <- x[, -2]
xt <- xtable(x, caption = c("R packages used in thesis as reported by \texttt{devtools::session\\_info()}", "R packages used in thesis"),
             label = "tab:R_packages")
align(xt) <- rep("c", ncol(x) + 1)
print(xt, booktabs = TRUE, comment = FALSE, tabular.environment = "longtable",
      floating = FALSE, include.rownames = FALSE, caption.placement = "top")
```
